PInSoRo: A Dataset for Deep-learning of Human-Robot Social Interactions

### 2017-06-28 paper.tex
Addressed Charlotte's comments

While the family of recurrent neural networks (RNNs) have repeatedly made the
headlines over the last few years with impressive results---notably in image
classification, image labelling and automatic translation---they have been so far 
%CERE: do these need references?
largely ignored by  many other fields as they are perceived to require very
large datasets (hundreds of thousands to millions of observations) to actually
build up useful capabilities. 
%CERE: perhaps this sentence could be shorter?
Even though neural networks have demonstrated
compelling results in open-ended, under-specified tasks like image labelling, they
did not stand out as attractive approaches to problems involving high dimensions
with relatively small datasets available -- like human-robot social
interactions.
Besides, if one considers ``social interactions'' to also entail joint
behavioural dynamics, and therefore, some sort of temporal modeling, neural
networks look even less enticing as time is notably absent from most of the
tasks which neural networks have been successful at.

@@

More recently, Ogata's team~\cite{yang2017repeatable} has demonstrated how an
adequately configured RNN is able to learn a complex robotic task (folding soft
objects like towels using a dual-arm mobile manipulator) from only \emph{35}
demonstrations of $\approx$ 70 seconds-long teleoperated
sequences. The network inputs are the raw video stream from the head camera and the
12 DoF of the two arms. Successfully folding towels entails an explicit sequencing of
%CERE: do you need to define DoF or is it obvious?
actions (therefore implicit temporal modeling). The fact that such a complex
process can be successfully learned from a small training dataset should lead
us to reconsider the range of domains to which RNNs would be applicable.

Indeed, as we have previously argued~\cite{lemaignan2016towards}, we believe
that the complexity of mechanisms that such neural networks have been able to
uncover and model should invite our community to explore its applicability to
%CERE: ``question'' to me seemed negative
human-robot interactions (HRI) in general, and sustained, natural child-robot
interactions in particular. However, the current lack of appropriate HRI
datasets suitable for neural networks training is an obstacle. In this article we introduce the PInSoRo dataset, a large dataset of child-child
natural interactions suitable for machine learning.

@@

The use of interaction datasets to teach robots how to socially behave has been
previously explored, and can be considered as the extension of the traditional
learning from demonstration (LfD) paradigms to social interactions (i.e.,~\cite{nehaniv2007imitation,mohammad2015interaction}). However, existing
research focuses on low-level identification or generation of short,
%CERE: ``recognition'' confused me as it's a type of memory paradigm -- possibly that's irrelevant to this audience though
self-standing behaviours, including social gestures~\cite{nagai2005learning}
and gazing behaviours~\cite{calinon2006teaching}.

@@

These examples show the burgeoning interest of our community for the automatic
learning of social interactions, but also highlight the lack of structured
research efforts, as further illustrated by the limited availability of large
and open datasets of social interactions, suitable for machine-learning
applications.
%CERE: you've already said most of this, perhaps it could be cut?

@@

%CERE: this didn't table for me?

>>>>

The family of recurrent neural networks (RNNs) have repeatedly made the
headlines over the last few years with impressive results---notably in image
classification, image labelling and automatic translation. They have been
however largely ignored by other fields as they are perceived to require
impossibly large datasets (hundreds of thousands to millions of observations) to
actually build up useful capabilities.  Even though neural networks have
demonstrated compelling results in open-ended, under-specified tasks like image
labelling, they did not stand out as attractive approaches to problems involving
high dimensions with relatively small datasets available -- like human-robot
social interactions.  Besides, if one considers ``social interactions'' to also
entail joint behavioural dynamics, and therefore, some sort of temporal
modeling, neural networks look even less enticing as time is notably absent from
most of the tasks which neural networks have been successful at.

@@

More recently, Ogata's team~\cite{yang2017repeatable} has demonstrated how an
adequately configured RNN is able to learn a complex robotic task (folding soft
objects like towels using a dual-arm mobile manipulator) from only \emph{35}
demonstrations of $\approx$ 70 seconds-long teleoperated
sequences. The network inputs are the raw video stream from the head camera and the
12 degrees of freedom of the two arms. Successfully folding towels entails an explicit sequencing of
actions (therefore implicit temporal modeling). The fact that such a complex
process can be successfully learned from a small training dataset should lead
us to reconsider the range of domains to which RNNs would be applicable.

Indeed, as we have previously argued~\cite{lemaignan2016towards}, we believe
that the complexity of mechanisms that such neural networks have been able to
uncover and model should invite our community to explore its applicability to
human-robot interactions (HRI) in general, and sustained, natural child-robot
interactions in particular.
%However, the current lack of appropriate HRI
%datasets suitable for neural networks training is an obstacle. In this article
%we introduce the PInSoRo dataset, a large dataset of child-child natural
%interactions suitable for machine learning.

@@

The use of interaction datasets to teach robots how to socially behave has been
previously explored, and can be considered as the extension of the traditional
learning from demonstration (LfD) paradigms to social interactions
(i.e.,~\cite{nehaniv2007imitation,mohammad2015interaction}). However, existing
research focuses on low-level identification or generation of short,
self-standing behaviours, including social gestures~\cite{nagai2005learning} and
gazing behaviours~\cite{calinon2006teaching}.

@@

These examples show the burgeoning interest of our community for the automatic
learning of social interactions, but also highlight the lack of structured
research efforts, as further illustrated by the limited availability of large
and open datasets of social interactions, suitable for machine-learning
applications.

@@
